---
title: "Shiny Application Presentation"
author: "Nicholas Ong"
date: "11/28/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Executive Summary

This is an assignment by John Hopkins University's Coursera Course - Developing Data Products - Week 4 Project. Below is the requirement:

- Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
- Deploy the application on Rstudio's shiny server
- Share the application link by pasting it into the provided text box
- Share your server.R and ui.R code on github

## Data - mtcars

The dataset is from standard R package - mtcars. For previewing the data, below is the code:

```{r mtcars dataset, echo = T}
head(mtcars)
```

- You could access the shiny webapp by clicking [here](https://huaigim.shinyapps.io/ShinyApplicationProject/).
- If you want to find out more information of the server.R and ui.R code, you could also visit my github repository [here](https://github.com/huaigim/JHU_DevelopingDataProducts_ShinyApplicationProject).

## Machine Learning Algorithm

Linear model is used to run the machine learning algorithm, to predict mileage per gallon based on variables selected by end-user.
- Below is an illustration using 'No. of cylinders' variable
- The output/ result will be stored in a variable called fit
```{r ml algo, echo = T}
fit <- lm(mpg ~ cyl, mtcars)
```

## Result

After running the model, the fit result and plot will be shown to the end-user
```{r result, echo = T}
with(mtcars, {plot(mpg ~ cyl)
        abline(fit, col = 2)})
fit
```

